---
title: "The 'survivalmodels' package"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(survivalmodels)
set.seed(42)
```

## What is the 'survivalmodels' package?

The `survivalmodels` package implements neural networks from the Python packages [pycox](https://github.com/havakv/pycox).  Importantly, this a lighter but CRAN-compatible version of the 'survivalmodels' package proposed by Raphael Sonabend based on the version 0.1.19. The complete and updated version is available at this [link](https://github.com/RaphaelS1/survivalmodels). 

## Basic Usage

```{r}
# load dependencies
library(survival)

train <- simsurvdata(200)

# Fit the survival neural network
fit <- deepsurv(Surv(time, status) ~ ., data = train, frac = 0.3, activation = "relu",
    num_nodes = c(4L, 8L, 4L, 2L), dropout = 0.1, early_stopping = TRUE, epochs = 100L,
    batch_size = 32L)

# Return survivals for two independent individuals
test <- simsurvdata(1)
predict(fit, newdata = test)
```

## Python Models

The `survivalmodels` package implements models from Python using [reticulate](https://cran.r-project.org/package=reticulate). In order to use these models, the required Python packages must be installed following with [reticulate::py_install](https://rstudio.github.io/reticulate/reference/py_install.html). `survivalmodels` includes a helper function to install the required `pycox` function (with pytorch if also required). Before running any models in this package, if you have not already installed `pycox` please run.

```{r eval=FALSE}
install_pycox(pip = TRUE, install_torch = FALSE)
```

## Installation

Install the latest release from CRAN:

```{r eval=FALSE}
install.packages("survivalmodels")
```

Install the development version from GitHub:

```{r eval=FALSE}
remotes::install_github("RaphaelS1/survivalmodels")
```
